---
title: "Procedural Learning 110320"
author: "Ola Ozernov-Palchik"
date: "11/4/2020"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r Clean and organize, include=FALSE,warning = FALSE}
# Clearn and organize data
#import packages 
Packages <- c("dplyr", "stats", "psych", "ggplot2", "lme4", 
              "gridExtra", "dplyr","caret","tidyverse", "ggplot2",
              "plyr","lmerTest","ggpubr","nlme","emmeans"
)

lapply(Packages, library, character.only = TRUE)
source("corstars_function.R")
####Organizational ####

#set subject directory 
#setwd("~/Dropbox (MIT)/learning_analysis")
setwd("~/Dropbox (MIT)/Github/procedural-learning")

#import pocedural.csv file
d <- read.csv('procedural_data072320.csv',stringsAsFactors = FALSE,skipNul = TRUE,
              blank.lines.skip = TRUE)



groups<-read.csv("abcd_group.csv")
names(groups)[names(groups)=="ID"] <- "PartID"
names(d)[names(d)=="abcd_id"] <- "PartID"
d<-merge(d,groups,'PartID')
SL=read.csv("sl_analysis/all_sl_wide.csv")

#Rename variables and organize

#exclude ineligible participants
d<-d%>%filter(d$PartID!='ABCD_1718')
d<-d%>%filter(d$PartID!='ABCD_1728')

d<-d%>%filter(d$Subgroup=="TYP"| d$Subgroup=="DD")

```

# Sample Size
```{r, echo=FALSE,warning = FALSE}
local({
  .Table <- xtabs(~Subgroup, data=d)
  cat("\nFrequency table:\n")
  print(.Table)
})
```


# Rotary Pursuit
####Question for JDE: Factor or continuous for trial?

```{r, include=FALSE}
## Extract and organize tasks
PL<-d[c(1,188,3:4,54:70,71:80)]

rp <- NULL
rp <- data.frame('PartID'= character(),'Subgroup' = character(),'plType' = character(),'trial' = double(),
                      'On' = double(),'Off' = double(),stringsAsFactors=FALSE)

for (i in 1:nrow(PL)) {
  if (PL[i,10] == ""){ #if null go to next line
    next()
  }
  for(k in 6:21){
    on <- as.numeric(trimws(strsplit(PL[i,k],';')[[1]][1]))
    off <- as.numeric(trimws(strsplit(PL[i,k],';')[[1]][2]))
    Subgroup <- PL[i,2]
    if (nrow(rp) == 0) {
      rp[1,] <- c(PL[i,1],as.character(PL[i,2]),'rp',k-5,on,off)    }
    else {
      rp[nrow(rp) + 1,] <- c(PL[i,1],as.character(PL[i,2]),'rp',k-5,on,off)
    }
  }
}

rp$On <- as.numeric(rp$On) 
rp$Off <- as.numeric(rp$Off)
rp$trial <- as.numeric(rp$trial) 

rp2<-rp%>%dplyr::group_by(PartID,Subgroup,trial)%>%
                         dplyr::mutate(prop_on=On/(On+Off))

plot(rp2$prop_on~rp2$trial)
 # left_join(d)

# Check # of trials per each subject
data_tmp4check <- aggregate(prop_on ~ PartID * Subgroup, FUN=NROW, data = rp2 )
unique(data_tmp4check[data_tmp4check$trial != 16,])
#View(data_tmp4check)
length(unique(d$PartID))
data_tmp4check[data_tmp4check$trial !=16,1]
hist(rp2$prop_on)
```

### Statstical Analysis by Trial

####There is a significant learning effect with increasing time on target on across trials. ####OOP::The problem with continuous trial that the interaction is significant at trial 8.47..not sure how to interpret.

```{r, echo=FALSE,warning = FALSE}
rp2$PartID = as.factor(rp2$PartID)
rp2$Subgroup = as.factor(rp2$Subgroup)
rp2$trial = as.numeric(as.character(rp2$trial)) # but then there is no learning effect?
m1<-lm(prop_on~Subgroup*trial,
        data=rp2) 
summary(m1) #sig group and trial. tried with age and sex, doesnt change the results
lsmeans(m1, list(pairwise ~ Subgroup|trial), adjust = "tukey")

```

###linear mixed-effect modeling: treating trial as a continuous variable
####OOP: i added model testing here. I would include Subject as random effects, but not trials.
```{r, echo=FALSE,warning = FALSE}
# library(lmerTest)
# #trial is not a sig random effect
# lmerrp1 <- lmer(prop_on~Subgroup*trial + (1|PartID),data=rp2)
# lmerrp2 <- lmer(prop_on~Subgroup*trial + (1+trial|PartID),data=rp2)
# anova(lmerrp1,lmerrp2)
# 
# #Subj is a sig random effect
# lmerrp3 <- lmer(prop_on~trial + (1|PartID),data=rp2)
# lmerrp4 <- lmer(prop_on~Subgroup*trial + (1+trial|PartID),data=rp2)
# anova(lmerrp3,lmerrp4)
# 
# print(summary(lmerrp)) #OOP:why differ when anova(model)
```

##Extract Slope
####growth curve analysis - ZQ note: the growth curve analyses suggested that the two groups are significantly different on the quadratic terms
```{r, echo=FALSE,warning = FALSE,include=FALSE}
temp = complete.cases(rp2)
rp2 = rp2[temp,]
s <- poly(unique(rp2$trial),2)
rp2[,paste("otrial",1:2,sep="")] <-s[rp2$trial,1:2]
summary(rp2)
m.base <- lmer(prop_on ~(otrial1+otrial2)+(otrial1+otrial2 | PartID),data=rp2,REML=FALSE)
m.0 <- lmer(prop_on ~(otrial1+otrial2)+ Subgroup + (otrial1+otrial2 | PartID),data=rp2,REML=FALSE)
m.1 <- lmer(prop_on ~(otrial1+otrial2)*Subgroup + (otrial1+otrial2 | PartID),data=rp2,REML=FALSE)
anova(m.base,m.0,m.1)
summary(m.1)
rp2$fitted_prop_on = fitted(m.1)
```

####Extract indiviudal slope
####OOP:Looks like the slopes are linear now
```{r, echo=FALSE}
# rp2$trial<-as.numeric(as.character(rp2$trial))
# m1<-lm(prop_on ~ poly(trial, 6, raw = TRUE), data = rp2) #determine how many terms
# summary(m1) #choose
# ggplot(rp2, aes(trial, prop_on) ) +
#   geom_point() +
#   stat_smooth(method = lm, formula = y ~ poly(x, 3, raw = TRUE))
```

```{r, echo=FALSE, include=FALSE}
d_glm_fit_list <- vector(mode = "list", length = nrow(rp)*2)
index <- 0
abcd_ids=unique(rp2$PartID)
b_list=c()
m_list = c()

for (subj in abcd_ids) { #d_export is my list of subject 
  #for (a in c("d", "b")) 
  # index <- index + 1
  #print(subj)
  d_subj <- filter(rp2, PartID==subj)
  subj_model <- lm(formula=On ~ trial, #complettion time(On/Off) ~trial
                    data = d_subj)
  b_list[subj] <- as.numeric(subj_model$coefficients[1]) # coefficient intercept
  m_list[subj] <- as.numeric(subj_model$coefficients[2]) # coefficient slope
  
}

#Off Slopes 
d_glm_fit_list <- vector(mode = "list", length = nrow(rp)*2)
index <- 0

abcd_ids=unique(rp$PartID)
b_list2=c()
m_list2 = c()

for (subj in abcd_ids) { #d_export is my list of subject 
  #for (a in c("d", "b")) 
  # index <- index + 1
  #print(subj)
  d_subj <- filter(rp2, PartID==subj)
  subj_model <- lm(formula=Off ~ poly(trial,3,raw=TRUE), #complettion time(On/Off) ~trial
                    data = d_subj)
  b_list2[subj] <- as.numeric(subj_model$coefficients[1]) # coefficient intercept
  m_list2[subj] <- as.numeric(subj_model$coefficients[2]) # coefficient slope
  
}

#PropOn Slopes

d_glm_fit_list <- vector(mode = "list", length = nrow(rp)*2)
index <- 0

abcd_ids=unique(rp$PartID)
b_list4=c()
m_list4 = c()
poly_list = c()

for (subj in abcd_ids) { #d_export is my list of subject 
  #for (a in c("d", "b")) 
  # index <- index + 1
  #print(subj)
  d_subj <- filter(rp2, PartID==subj)
  subj_model <- lm(formula=prop_on ~ trial, #complettion time(On/Off) ~trial
                    data = d_subj)
  b_list4[subj] <- as.numeric(subj_model$coefficients[1]) # coefficient intercept
  m_list4[subj] <- as.numeric(subj_model$coefficients[2]) # coefficient slope
}

#Creat a new Data Frame containing the slopes
rp_data <- data.frame(PartID=abcd_ids,slopeOn = m_list, slopeOff = m_list2, slopeProp_On = m_list4)
rp_data$slopeProp_On<-as.numeric(rp_data$slopeProp_On)
d_rp<-merge(d,rp_data)
```

```{r, echo=FALSE}
hist(d_rp$slopeProp_On)
```


## Plot task

###Prop On by Trial
```{r, echo=FALSE,warning = FALSE}
rp2$trial<-as.integer(rp2$trial)

rpPlot<-dplyr::summarise(group_by(rp2,Subgroup,trial), n = n(),
                         mean=mean(prop_on,na.rm = T), sd=sd(On/(On+Off),na.rm = T),se = sd/sqrt(n))

ggplot(data = rpPlot, aes(x=trial, y=mean, color = Subgroup))+
  geom_line() +geom_point()  +
  scale_color_manual(values=c('red','blue'))+
  geom_errorbar(aes(ymin=mean-se,ymax=mean+se),
                 width=.1,  size=0.5)+
  scale_x_continuous(breaks=seq(2,16,1))+
  #scale_y_continuous(limits = c(0.2, 0.5))+
  theme(
    axis.title = element_text(family = "Trebuchet MS", size = 20),
    legend.key.size = unit(1, "cm"),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15))  + 
  labs(x = "Trials", y = "Proportion On (secs)") +
  theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
  theme(axis.line = element_line(arrow = arrow(angle = 15, length = unit(.15,"inches"),type = "closed")))
```
### alternative plots with fitted curve
####OOP: this doesn't work for me
```{r, echo=FALSE,warning = FALSE, include=FALSE}
ggplot(rp2, aes(trial, prop_on, color=Subgroup))+
  stat_summary(fun.data=mean_se, geom="pointrange")+
  stat_summary(aes(y=fitted_prop_on),fun.y=mean, geom="line")+
  scale_color_manual(values=c('red','blue'))+
  scale_x_continuous(breaks=seq(2,16,1))+
  theme(
    axis.title = element_text(family = "Trebuchet MS", size = 20),
    legend.key.size = unit(1, "cm"),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15))  + 
  labs(x = "Trials", y = "Proportion On (secs)") +
  theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
  theme(axis.line = element_line(arrow = arrow(angle = 15, length = unit(.15,"inches"),type = "closed")))
```

###Slope Analysis- No significant effects for RP slopes
```{r, echo=FALSE,warning = FALSE}
m2<-lm(slopeProp_On~background_age+background_sex+Subgroup, data=d_rp)
anova(m2)
lsmeans(m2, list(pairwise ~ Subgroup), adjust = "tukey")

```

###Slope Effects
```{r, echo=FALSE,warning = FALSE}
plot_rp_slope<-d_rp%>%dplyr::select('PartID',"Subgroup","slopeProp_On")
plot_rp_slope<-na.omit(plot_rp_slope)
rp_slope = plot_rp_slope %>%
  dplyr::group_by(PartID, Subgroup) %>%
  dplyr::summarise(mean = mean(slopeProp_On, na.rm = T))

multi.group3 <- 
  rp_slope %>%
  dabestr::dabest(Subgroup,mean, 
         idx = list(c("TYP",'DD')),
         paired = FALSE)
plot(multi.group3, palette=c("blue","red"),rawplot.ylabel = "RP Prop On Slope")
```

# Mirror Tracing


```{r, include=FALSE,warning = FALSE}
## Extract and organize
mt <- NULL
mt <- data.frame('PartID'= character(),'Subgroup' = character(),'Type' = character(),'trial' = double(),
                     'time' = double(),'error' = double(),stringsAsFactors=FALSE)
for (i in 1:nrow(PL)) {
  if (PL[i,22] == ""){ #if null go to next line
    next()
  }
  for(k in 22:31){
    print(paste(k,PL[i,k]))
    time <- as.numeric(trimws(strsplit(PL[i,k],';')[[1]][1]))
    error <- as.numeric(trimws(strsplit(PL[i,k],';')[[1]][2]))
    if (nrow(mt) == 0) {
      mt[1,] <- c(PL[i,1],PL[i,2],'mt',k-21,time,error)
    }
    else {
      mt[nrow(mt) + 1,] <- c(PL[i,1],PL[i,2],'mt',k-21,time,error)
    }
  }
}

mt$time <- as.numeric(mt$time) 
mt$error <- as.numeric(mt$error)
mt$trial <- as.numeric(mt$trial)
```
## QC
#### John: should we exclude outliers?
```{r,include=FALSE}
# Check # of trials per each subject
data_tmp4check <- aggregate(error ~ PartID * Subgroup, FUN=NROW, data = mt )
unique(data_tmp4check[data_tmp4check$trial != 10,])
#View(data_tmp4check)
length(unique(d$PartID))
data_tmp4check[data_tmp4check$trial !=10,1]

# Outliers
summary(mt)
mt2<-mt%>%filter(time<200) #excluded 2
mt2<-mt #place holder while deciding on outliers
length(unique(mt$PartID))
length(unique(mt2$PartID))
histogram(mt2$error)
histogram(mt2$time)
```


##MT: Analysis: 
```{r, echo=FALSE,warning = FALSE}
m3<-lm(time~Subgroup*trial,
        data=mt2)
summary(m3) #trial+subgroup are significant
lsmeans(m3, list(pairwise ~ Subgroup|trial), adjust = "tukey")


m4<-lm(error~Subgroup*trial,
        data=mt2)

anova(m4)
lsmeans(m4, list(pairwise ~ Subgroup|trial), adjust = "tukey")

```

```{r, echo=FALSE,warning = FALSE}
lmerm1<-lmer(time~Subgroup*trial+(1+trial|PartID),
        data=mt2)
summary(lmerm1)
```

####Need to decide on whether we want lme models
```{r, echo=FALSE,warning = FALSE}
lmerm2<-lmer(error~Subgroup*trial+(1+trial|PartID),
        data=mt2)
summary(lmerm2)
```
## MT: Plot Time/Error by Trial

```{r, echo=FALSE,warning = FALSE}
mt2$time <- as.numeric(mt2$time) 
mt2$error <- as.numeric(mt2$error)
mt2$trial <- as.numeric(mt2$trial)

mtTPlot<-dplyr::summarise(group_by(mt2,Subgroup,trial), n = n(),
                         meanT=mean(time,na.rm = T), sd=sd(time,na.rm = T),se = sd/sqrt(n))
mtEPlot<-dplyr::summarise(group_by(mt2,Subgroup,trial), n = n(),
                          meanE=mean(error,na.rm = T), sd=sd(error,na.rm = T),se = sd/sqrt(n))


ggplot(data = mtTPlot, aes(x=trial, y=meanT, color = Subgroup))+
  geom_line() +geom_point()  +
  scale_color_manual(values=c('red','blue'))+
  geom_errorbar(aes(ymin=meanT-se,ymax=meanT+se),
                width=.1,  size=0.5)+
  scale_x_continuous(breaks=seq(0,10,1))+
  #scale_y_continuous(limits = c(0.2, 0.5))+
  theme(
    axis.title = element_text(family = "Trebuchet MS", size = 20),
    legend.key.size = unit(1, "cm"),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15))  + 
  labs(x = "Trials", y = "Completion Time (secs)") +
  theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
  theme(axis.line = element_line(arrow = arrow(angle = 15, length = unit(.15,"inches"),type = "closed")))
```


```{r, echo=FALSE,warning = FALSE}
ggplot(data = mtEPlot, aes(x=trial, y=meanE, color = Subgroup))+
  geom_line() +geom_point()  +
  scale_color_manual(values=c('red','blue'))+
  geom_errorbar(aes(ymin=meanE-se,ymax=meanE+se),
                width=.1,  size=0.5)+
  scale_x_continuous(breaks=seq(0,10,1))+
  #scale_y_continuous(limits = c(0.2, 0.5))+
  theme(
    axis.title = element_text(family = "Trebuchet MS", size = 20),
    legend.key.size = unit(1, "cm"),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15))  + 
  labs(x = "Trials", y = "Errors") +
  theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
  theme(axis.line = element_line(arrow = arrow(angle = 15, length = unit(.15,"inches"),type = "closed")))
```

##Mirror Tracing Slopes
### growth curve analysis suggested the two groups are signficiantly different on quardratic terms
#### completion time
```{r, echo=FALSE}
temp = complete.cases(mt2)
mt2 = mt2[temp,]
s <- poly(unique(mt2$trial),2)
mt2[,paste("otrial",1:2,sep="")] <-s[mt2$trial,1:2]
summary(mt2)
m.base <- lmer(time ~(otrial1+otrial2)+(otrial1+otrial2 | PartID),data=mt2,REML=FALSE)
m.0 <- lmer(time ~(otrial1+otrial2)+ Subgroup + (otrial1+otrial2 | PartID),data=mt2,REML=FALSE)
m.1 <- lmer(time ~(otrial1+otrial2)*Subgroup + (otrial1+otrial2 | PartID),data=mt2,REML=FALSE)
anova(m.base,m.0,m.1)
summary(m.1)
mt2$fitted_time=fitted(m.1)
```
#### errors
```{r, echo=FALSE}
m.base <- lmer(error ~(otrial1+otrial2)+(otrial1+otrial2 | PartID),data=mt2,REML=FALSE)
m.0 <- lmer(error ~(otrial1+otrial2)+ Subgroup + (otrial1+otrial2 | PartID),data=mt2,REML=FALSE)
m.1 <- lmer(error ~(otrial1+otrial2)*Subgroup + (otrial1+otrial2 | PartID),data=mt2,REML=FALSE)
anova(m.base,m.0,m.1)
summary(m.1)
mt2$fitted_error=fitted(m.1)
```

```{r, echo=FALSE}
hist(mt$error)
lm(error ~ poly(trial, 2, raw = TRUE), data = mt2) %>%
  summary() #chose 2

lm(time ~ poly(trial, 3, raw = TRUE), data = mt2) %>%
  summary() #chose 3
```
#### fit polynomial curves for the MT time plots
```{r, echo=FALSE}
ggplot(mt2, aes(trial, time, color=Subgroup))+
  stat_summary(fun.data=mean_se, geom="pointrange")+
  stat_summary(aes(y=fitted_time), geom="line")+
  scale_color_manual(values=c('red','blue'))+
  scale_x_continuous(breaks=seq(2,16,1))+
  theme(
    axis.title = element_text(family = "Trebuchet MS", size = 20),
    legend.key.size = unit(1, "cm"),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15))  + 
  labs(x = "Trials", y = "Completion Time (secs)") +
  theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
  theme(axis.line = element_line(arrow = arrow(angle = 15, length = unit(.15,"inches"),type = "closed")))
```
#### fit polynomial curves for the MT error plots
```{r, echo=FALSE}
ggplot(mt2, aes(trial, error, color=Subgroup))+
  stat_summary(fun.data=mean_se, geom="pointrange")+
  stat_summary(aes(y=fitted_error), geom="line")+
  scale_color_manual(values=c('red','blue'))+
  scale_x_continuous(breaks=seq(2,16,1))+
  theme(
    axis.title = element_text(family = "Trebuchet MS", size = 20),
    legend.key.size = unit(1, "cm"),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15))  + 
  labs(x = "Trials", y = "Error") +
  theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
  theme(axis.line = element_line(arrow = arrow(angle = 15, length = unit(.15,"inches"),type = "closed")))
```


### Extract slopes

```{r, echo=FALSE,warning = FALSE}

#Error slopes
d_glm_fit_list <- vector(mode = "list", length = nrow(rp)*2)
index <- 0
abcd_ids=unique(mt2$PartID)
b_list5=c()
m_list5 = c()

for (subj in abcd_ids) {
 # print(subj)
  d_subj <- filter(mt, PartID==subj)
  subj_model <- glm(error ~ trial, #errors
                    data = d_subj)
  b_list5[subj] <- as.numeric(subj_model$coefficients[1]) # coefficient intercept
  m_list5[subj] <- as.numeric(subj_model$coefficients[2]) # coefficient slope
}
```


```{r, echo=FALSE,warning = FALSE}
d_glm_fit_list <- vector(mode = "list", length = nrow(rp)*2)
index <- 0
abcd_ids=unique(mt2$PartID)
b_list7=c()
m_list7 = c()

for (subj in abcd_ids) { #d_export is my list of subject 
  #print(subj)
  d_subj <- dplyr::filter(mt2, PartID==subj)
  subj_model <- lm(formula=time ~ poly(trial,4,raw=TRUE), #completion time
                    data = d_subj)
  b_list7[subj] <- as.numeric(subj_model$coefficients[1]) # coefficient intercept
  m_list7[subj] <- as.numeric(subj_model$coefficients[2]) # coefficient slope
  
}


#new data frame containing the mirror slopes
mt_data <- data.frame(PartID=abcd_ids,slope_me = m_list5, slope_mt = m_list7)
mt_data$slope_mt<-as.numeric(mt_data$slope_mt)
mt_data=mt_data%>%dplyr::filter(slope_me>-300)
mt_data$slope_me<-log(abs(mt_data$slope_me)) #transform slope
hist(mt_data$slope_me)
d2<-merge(d, mt_data)
```

```{r, echo=FALSE,warning = FALSE} 
d_glm_fit_list <- vector(mode = "list", length = nrow(rp)*2)
index <- 0
abcd_ids=unique(mt2$PartID)
b_list7=c()
m_list7 = c()

for (subj in abcd_ids) { #d_export is my list of subject 
  #print(subj)
  d_subj <- dplyr::filter(mt, PartID==subj)
  subj_model <- glm(time ~ trial, #complettion time(On/Off) ~trial
                    data = d_subj,na.action = 'na.omit')
  b_list7[subj] <- as.numeric(subj_model$coefficients[1]) # coefficient intercept
  m_list7[subj] <- as.numeric(subj_model$coefficients[2]) # coefficient slope
  
}

#new data frame containing the mirror slopes
mt_data <- data.frame(PartID=abcd_ids,slope_me = m_list5, slope_mt = m_list7)
mt_data<-as.data.frame(mt_data)
mt_data$slope_me_t<-abs(as.numeric(mt_data$slope_me))
mt_data$slope_me_t<-log10(mt_data$slope_me_t+1) #transform slope
#mt_data<-mt_data%>%filter(slope_me_t!="-Inf") #transform slope

mt_data$slope_mt_t<-abs(as.numeric(mt_data$slope_mt))
mt_data$slope_mt_t<-log10(mt_data$slope_mt_t) #transform slope

d_3 <- d %>%
   select("PartID","Subgroup", "background_age","background_sex")

d_mt <- left_join(mt_data, d_3, by = "PartID")
d2<-merge(d_rp,d_mt)
```

###MT: Slope Analysis
```{r, echo=FALSE,warning = FALSE}
#t.test(d_mt$slope_mt_t~d_mt$Subgroup)
#t.test(d_mt$slope_me_t~d_mt$Subgroup)

m3<-lm(slope_mt_t~background_age+background_sex+Subgroup, data=d_mt,na.action = na.exclude)
anova(m3)
m4<-lm(slope_me_t~background_age+background_sex+Subgroup, data=d_mt,na.action = na.exclude)
anova(m4) #sig group difference
lsmeans(m4, list(pairwise ~ Subgroup), adjust = "tukey")

```
## MT: Plot Slope Effects

```{r, echo=FALSE,warning = FALSE}
mt_slope<-d2%>%dplyr::select("PartID","Subgroup","slope_mt_t")

mt_slope = mt_slope %>%
  dplyr::group_by(PartID, Subgroup) %>%
  dplyr::summarise(mean = mean(slope_mt_t, na.rm = T))

multi.group_mt <- 
 mt_slope %>%
  dabestr::dabest(Subgroup,mean, 
         idx = list(c("TYP","DD")),
         paired = FALSE
  )

plot(multi.group_mt, palette=c("blue","red"),rawplot.ylabel = "MT Time Slope")


```
```{r, echo=FALSE,warning = FALSE}
me_slope<-d2%>%dplyr::select("PartID","Subgroup","slope_me_t")

me_slope = me_slope %>%
  dplyr::group_by(PartID, Subgroup) %>%
  dplyr::summarise(mean = mean(slope_me_t, na.rm = T))

multi.group_me <- 
 me_slope %>%
  dabestr::dabest(Subgroup,mean, 
         idx = list(c("TYP","DD")),
         paired = FALSE
  )

plot(multi.group_me, palette=c("blue","red"),rawplot.ylabel = "MT Time Slope")
```

# Statistical Learning
```{r, echo=FALSE,warning = FALSE}
names(SL)[names(SL) == "subj"] <- "PartID"
d_all<-merge(d,rp_data,all = TRUE)
d_all <-merge(d_all,mt_data,all=TRUE)
d_all <-merge(d_all,SL,all=TRUE)
table(SL$group)
```

## Slope analyses (ZQ notes: the group difference analysis should refer to abcd_sl_analysis.pdf)
```{r,echo=FALSE,warning = FALSE}
m5<-lm(aud_slope_scale~background_age+background_sex+Subgroup, data=d_all,na.action = na.exclude)
anova(m5) #sig group difference
```

##ASL Slope Effects (ZQ notes: the group difference analysis should refer to abcd_sl_analysis.pdf)


```{r, echo=FALSE,warning = FALSE}
asl_slope<-d_all%>%dplyr::select("PartID","Subgroup","aud_slope_scale")

asl_slope<-na.omit(asl_slope)

asl_slope2 = asl_slope %>%
  dplyr::group_by(PartID, Subgroup) %>%
  dplyr::summarise(mean = mean(aud_slope_scale, na.rm = T))

multi.group_asl <- 
 asl_slope2 %>%
  dabestr::dabest(Subgroup,mean, 
         idx = list(c("TYP","DD")),
         paired = FALSE
  )

plot(multi.group_asl, palette=c("blue","red"),rawplot.ylabel = "ASL Time Slope")


```

##VSL Slope Analysis (ZQ notes: the group difference analysis should refer to abcd_sl_analysis.pdf)
```{r,echo=FALSE,warning = FALSE}
m6<-lm(vis_slope_scale~background_age+background_sex+Subgroup, data=d_all,na.action = na.exclude)
anova(m6) #sig group difference
```

##VSL Effect Plot (ZQ notes: the group difference analysis should refer to abcd_sl_analysis.pdf, significant group effect)
```{r, echo=FALSE,warning = FALSE}
vsl_slope<-d_all%>%dplyr::select("PartID","Subgroup","vis_slope_scale")

vsl_slope<-na.omit(vsl_slope)

vsl_slope2 = vsl_slope %>%
  dplyr::group_by(PartID, Subgroup) %>%
  dplyr::summarise(mean = mean(vis_slope_scale, na.rm = T))

multi.group_vsl <- 
 vsl_slope2 %>%
  dabestr::dabest(Subgroup,mean, 
         idx = list(c("TYP","DD")),
         paired = FALSE
  )

plot(multi.group_vsl, palette=c("blue","red"),rawplot.ylabel = "VSL Slope")

```
##RT Slope
```{r,echo=FALSE,warning = FALSE}
m6<-lm(aud_fam_rt~background_age+background_sex+Subgroup, data=d_all,na.action = na.exclude)
anova(m6) 

m7<-lm(vis_fam_rt~background_age+background_sex+Subgroup, data=d_all,na.action = na.exclude)
anova(m7) 
```

###Cross-task correlations
```{r,include=FALSE,warning = FALSE}
d_all_dys = subset(d_all,Subgroup == "DD")
d_all_typ = subset(d_all,Subgroup == "TYP")
task_data<-d_all%>%select(kbit_ss_2,gort_ori_ss_2,ctopp_nonword_raw_2,ctopp_elision_raw_2,ctopp_blending_raw_2,wais_dsb_ss_2,slopeProp_On,slope_mt_t,slope_me_t,vis_slope_scale,aud_slope_scale,quicksin_snr_loss_2)
task_data_dys<-d_all_dys%>%select(wrmt_id_ss_2,wrmt_wa_ss_2,towre_sw_ss_2,towre_pde_ss_2, slopeProp_On, slope_mt,slope_me,aud_acc,vis_acc,aud_slope_scale,vis_slope_scale)
task_data_typ<-d_all_typ%>%select(wrmt_id_ss_2,wrmt_wa_ss_2,towre_sw_ss_2,towre_pde_ss_2, slopeProp_On,slope_mt,slope_me,aud_acc,vis_acc,aud_slope_scale,vis_slope_scale)
corstars(task_data,method="pearson")#you need to run the function first
```

###Everyone
```{r, echo=FALSE}
corstars(task_data,method="pearson")#you need to run the function first

```
###Dys only

```{r, echo=FALSE}
corstars(task_data_dys,method="pearson")#you need to run the function first
```

###Typ only
```{r, echo=FALSE}
corstars(task_data_typ,method="pearson")#you need to run the function first
```
