---
title: "ABCD Analysis"
author: "Zhenghan Qi"
date: "July 24, 2020"
output:
  pdf_document: default
  html_document: default
---
```{r,echo=FALSE,warning=FALSE}
#Loading library
library(ggplot2)
library(knitr)
library(readr)
library(reshape)
library(reshape2)
library(lmerTest)
library(scales)
library(ggbeeswarm)
library(Hmisc)
library(ggbeeswarm)
```

```{r,echo=FALSE}
#Initialize variables
total_participant <- 40 #40 vsl participants and 40 tsl participants
total_vsl_trial <- 24 #number of trials in the familiarization block
total_tsl_trial <- 48
length_vsl <- 533 #number of rows in a vsl excel file
length_tsl <- 832 #number of rows in a tsl excel file
total_test_trial <- 32
```


```{r,echo=FALSE}
#Note: The code below is to work on the raw files to combine them. You can import the already combined vsl from /abcd/raw/summary/vsl.csv and tsl files if you just want to look at the analysis part.

#importing raw files
tsl <- list()
vsl <- list()
vsl_par_id <- NULL
tsl_par_id <- NULL
path <- "/Users/zhenghanqi/Dropbox (MIT)/UDel/projects/collaboration/abcd/raw/"  
files <- list.files(path=path, pattern="*tsl.csv") 
vsl_files <- list.files(path=path, pattern="*vsl.csv")

for(file in files)
{
   
    assign(
        gsub(" ","",file), 
        read.csv(paste(path,file,sep="")))
}
for(file in files){tsl <- append(tsl,list(eval(parse(text=file))))}

for(vslfile in vsl_files)
{
    assign(
        gsub(" ","",vslfile), 
        read.csv(paste(path,vslfile,sep="")))
}
for(text in vsl_files){vsl <- append(vsl,list(eval(parse(text=text))))}

vsl <- do.call(rbind.data.frame, vsl)
tsl <- do.call(rbind.data.frame, tsl)

#add an ID column for each row
for (i in seq(from=1,to=length(vsl$responses),by=length_vsl)){vsl_par_id<-append(vsl_par_id,rep(substr(vsl$responses[i],8,16),length_vsl))}
for (i in seq(from=1,to=length(tsl$responses),by=length_tsl)){tsl_par_id<-append(tsl_par_id,rep(substr(tsl$responses[i],8,16),length_tsl))}
vsl$par_id <- vsl_par_id
tsl$par_id <- tsl_par_id

#Group set up: 17 DD and 24 TYP
DD <- list("ABCD_1711", "ABCD_1714", "ABCD_1727", "ABCD_1735", "ABCD_1751", "ABCD_1756", "ABCD_1764", "ABCD_1767", "ABCD_1768", "ABCD_1776","ABCD_1777","ABCD_1778", "ABCD_1781", "ABCD_1784", "ABCD_1787", "ABCD_1792", "ABCD_1794")

TYP <- list("ABCD_1702", "ABCD_1703", "ABCD_1705", "ABCD_1708", "ABCD_1709", "ABCD_1710", "ABCD_1716", "ABCD_1720", "ABCD_1721", "ABCD_1724", "ABCD_1725", "ABCD_1728", "ABCD_1729", "ABCD_1730", "ABCD_1732", "ABCD_1734", "ABCD_1736", "ABCD_1739", "ABCD_1742", "ABCD_1747", "ABCD_1749", "ABCD_1754", "ABCD_1783", "ABCD_1788" )
group <- NULL
for (i in seq(from=1,to=length(tsl$par_id),by=1))
    {if (tsl[i,]$par_id %in% TYP)
    {group[i]<-"TYP"}
    else if (tsl[i,]$par_id %in% DD)
    {group[i] <- "DD"}}
tsl$group <- group
groupv <- NULL
for (i in seq(from=1,to=length(vsl$par_id),by=1))
    {if (vsl[i,]$par_id %in% TYP)
    {groupv[i]<-"TYP"}
    else if (vsl[i,]$par_id %in% DD)
    {groupv[i] <- "DD"}}
vsl$group <- groupv


#Get the ID of every participant
list_tsl_id <- unique(tsl$par_id)
list_vsl_id <- unique(vsl$par_id)


language_1 = list(1,2,2,2,1,1,2,1,1,2,1,2,1,1,2,2,1,1,2,1,2,2,1,2,2,2,1,2,1,2,1,1)
language_2 = list(1,1,2,1,1,1,2,2,2,2,1,1,1,2,2,1,2,2,1,1,2,1,2,1,2,1,2,1,1,2,2,2)
```

```{r,echo=FALSE}
#Clean data: remove file extension and path of the stimuli so the format of the stimuli match with the target

vsl$stimulus<- gsub(".jpg","",vsl$stimulus)
vsl$stimulus<- gsub("../../images/","",vsl$stimulus)

tsl$stimulus<- gsub(".wav","",tsl$stimulus)
tsl$stimulus<- gsub("../../tones/","",tsl$stimulus)
```

#Compute RT for VSL
* two groups are not different in target detection d-prime
* the DD group showed a significantly negative RT slope
* the TYP group showed a nonsignificantly negative RT slope
```{r,echo=FALSE}
compute_visual <- function(data)
{
rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
group_cond <- NULL

row_number <- which(vsl$targ==vsl$stimulus) #extract rows in which stimuli match with target
for (i in row_number){
        rt_col <- append(rt_col,vsl[i,][,"rt"])
        trial <- append(trial,vsl[i,][,"trial_index"])
        id <- append(id,vsl[i,]$par_id)
        group_cond <- append(group_cond,vsl[i,]$group)
    if (vsl[i-1,][,"rt"]!=-1){
        rt_col[(match(i,row_number))] <- -(1000-vsl[i-1,][,"rt"])
    }}

rt_df1 <- data.frame(trial,rt_col,id,group_cond) 
#NOTE: Depending on your version of R and your setting, the lines below may run inaccurately. You can check type rt_df1 after running this line to check if it returns a correct data frame. If not, run these two lines instead: 
#rt_df1 <- data.frame(unlist(trial),unlist(rt_col),id,group_cond) 
#colnames(rt_df1) <- c("trial","rt_col","id","group_cond")

fam_block <- vsl[which(vsl$trial_index<=300 & vsl$trial_index>=12),] #the familiarization block starts with index number 13 and ends with index 300
fam_trial <- rt_df1[which(rt_df1$trial<=300 & rt_df1$trial>=12), ]
reindex <- rep(1:total_vsl_trial,total_participant)
fam_trial$reindex <- reindex
fam_trial <- fam_trial[which(!is.na(fam_trial$group_cond)),]

hit_rate <- NULL
miss_rate <- NULL
correct_rejection <- NULL
false_alarm <- NULL
mean_rt <- NULL
rt_slope <- NULL
mean_table <- fam_trial[which(fam_trial$rt_col!=-1 & fam_trial$rt_col<1000 & fam_trial$rt_col>-1000), ] #only accept answers in range of -1000 < x < 1000

list_vsl_id <- unique(mean_table$id)

for(id in list_vsl_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
  hit_rate<-append(hit_rate,round(sum(!is.na(mean_table$rt_col[mean_table$id==id]))/total_vsl_trial,digits =2))
  miss_rate<-append(miss_rate,round(sum(fam_trial$rt_col[fam_trial$id==id]==-1)/total_vsl_trial,digits=2))
  correct_rejection <- append(correct_rejection, round(sum(fam_block$rt[fam_block$par_id==id]==-1 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/264,digits=3)) #264 is the total number of stimuli in the familiarization block
  false_alarm <- append(false_alarm, round(sum(fam_block$rt[fam_block$par_id==id]!=-1 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/264,digits=3))
}

subj_table <- data.frame(list_vsl_id,mean_rt, rt_slope,hit_rate, miss_rate,correct_rejection,false_alarm)
dprime<-NULL
for (i in seq(from=1,to=length(subj_table$list_vsl_id),by=1)){dprime<-append(dprime,qnorm(subj_table[i,]$hit_rate-0.00000001)-qnorm(subj_table[i,]$false_alarm+0.000000001))} #minus 0.000000001 to avoid perfect hit rate
subj_table$dprime <- dprime

#colnames(subj_table) <- c("VSL_ID","mean_rt", "rt_slope","hit", "miss","corr_rejection","false_alarm","dprime")
#print(kable(subj_table,format = "pandoc"))

group <- NULL
for (i in seq(from=1,to=length(subj_table$list_vsl_id),by=1))
    {if (subj_table[i,]$list_vsl_id %in% TYP)
    {group[i]<-"TYP"}
    else if (subj_table[i,]$list_vsl_id %in% DD)
    {group[i] <- "DD"}}
subj_table$group <- group

vrtdd <- t.test(subj_table$rt_slope[subj_table$group=="DD"],mu=0,alternative="less")
vrttyp <- t.test(subj_table$rt_slope[subj_table$group=="TYP"],mu=0,alternative="less")
vdd_v_typ <- t.test(rt_slope~group,data=subj_table)
model3 <- wilcox.test(dprime~group,data=subj_table)
model4 <- wilcox.test(mean_rt~group,data=subj_table)
print(model3)
print(model4)
print(vrtdd)
print(vrttyp)
return(mean_table)
}

compute_visual_scale <- function(data)
{
rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
group_cond <- NULL

row_number <- which(vsl$targ==vsl$stimulus) #extract rows in which stimuli match with target
for (i in row_number){
        rt_col <- append(rt_col,vsl[i,][,"rt"])
        trial <- append(trial,vsl[i,][,"trial_index"])
        id <- append(id,vsl[i,]$par_id)
        group_cond <- append(group_cond,vsl[i,]$group)
    if (vsl[i-1,][,"rt"]!=-1){
        rt_col[(match(i,row_number))] <- -(1000-vsl[i-1,][,"rt"])
    }}

rt_df1 <- data.frame(trial,rt_col,id,group_cond) 
#NOTE: Depending on your version of R and your setting, the lines below may run inaccurately. You can check type rt_df1 after running this line to check if it returns a correct data frame. If not, run these two lines instead: 
#rt_df1 <- data.frame(unlist(trial),unlist(rt_col),id,group_cond) 
#colnames(rt_df1) <- c("trial","rt_col","id","group_cond")

fam_block <- vsl[which(vsl$trial_index<=300 & vsl$trial_index>=12),] #the familiarization block starts with index number 13 and ends with index 300
fam_trial <- rt_df1[which(rt_df1$trial<=300 & rt_df1$trial>=12), ]
reindex <- rep(1:total_vsl_trial,total_participant)
fam_trial$reindex <- reindex
fam_trial <- fam_trial[which(!is.na(fam_trial$group_cond)),]

hit_rate <- NULL
miss_rate <- NULL
correct_rejection <- NULL
false_alarm <- NULL
mean_rt <- NULL
rt_slope <- NULL
mean_table <- fam_trial[which(fam_trial$rt_col!=-1 & fam_trial$rt_col<1000 & fam_trial$rt_col>-1000), ] #only accept answers in range of -1000 < x < 1000

list_vsl_id <- unique(mean_table$id)

for(id in list_vsl_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  # normalize each participant's RT
  mean_table$rt_col[mean_table$id==id] = scale(mean_table$rt_col[mean_table$id==id])
  rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
  hit_rate<-append(hit_rate,round(sum(!is.na(mean_table$rt_col[mean_table$id==id]))/total_vsl_trial,digits =2))
  miss_rate<-append(miss_rate,round(sum(fam_trial$rt_col[fam_trial$id==id]==-1)/total_vsl_trial,digits=2))
  correct_rejection <- append(correct_rejection, round(sum(fam_block$rt[fam_block$par_id==id]==-1 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/264,digits=3)) #264 is the total number of stimuli in the familiarization block
  false_alarm <- append(false_alarm, round(sum(fam_block$rt[fam_block$par_id==id]!=-1 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/264,digits=3))
}

subj_table <- data.frame(list_vsl_id,mean_rt, rt_slope,hit_rate, miss_rate,correct_rejection,false_alarm)
dprime<-NULL
for (i in seq(from=1,to=length(subj_table$list_vsl_id),by=1)){dprime<-append(dprime,qnorm(subj_table[i,]$hit_rate-0.00000001)-qnorm(subj_table[i,]$false_alarm+0.000000001))} #minus 0.000000001 to avoid perfect hit rate
subj_table$dprime <- dprime

#colnames(subj_table) <- c("VSL_ID","mean_rt", "rt_slope","hit", "miss","corr_rejection","false_alarm","dprime")
#print(kable(subj_table,format = "pandoc"))

group <- NULL
for (i in seq(from=1,to=length(subj_table$list_vsl_id),by=1))
    {if (subj_table[i,]$list_vsl_id %in% TYP)
    {group[i]<-"TYP"}
    else if (subj_table[i,]$list_vsl_id %in% DD)
    {group[i] <- "DD"}}
subj_table$group <- group

return(mean_table)
}

get_subj_visual <- function(data)
{
rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
group_cond <- NULL

row_number <- which(vsl$targ==vsl$stimulus) #extract rows in which stimuli match with target
for (i in row_number){
        rt_col <- append(rt_col,vsl[i,][,"rt"])
        trial <- append(trial,vsl[i,][,"trial_index"])
        id <- append(id,vsl[i,]$par_id)
        group_cond <- append(group_cond,vsl[i,]$group)
    if (vsl[i-1,][,"rt"]!=-1){
        rt_col[(match(i,row_number))] <- -(1000-vsl[i-1,][,"rt"])
    }}

rt_df1 <- data.frame(trial,rt_col,id,group_cond) 
#NOTE: Depending on your version of R and your setting, the lines below may run inaccurately. You can check type rt_df1 after running this line to check if it returns a correct data frame. If not, run these two lines instead: 
#rt_df1 <- data.frame(unlist(trial),unlist(rt_col),id,group_cond) 
#colnames(rt_df1) <- c("trial","rt_col","id","group_cond")

fam_block <- vsl[which(vsl$trial_index<=300 & vsl$trial_index>=12),] #the familiarization block starts with index number 13 and ends with index 300
fam_trial <- rt_df1[which(rt_df1$trial<=300 & rt_df1$trial>=12), ]
reindex <- rep(1:total_vsl_trial,total_participant)
fam_trial$reindex <- reindex
fam_trial <- fam_trial[which(!is.na(fam_trial$group_cond)),]

hit_rate <- NULL
miss_rate <- NULL
correct_rejection <- NULL
false_alarm <- NULL
mean_rt <- NULL
rt_slope <- NULL
rt_slope_scale <- NULL
mean_table <- fam_trial[which(fam_trial$rt_col!=-1 & fam_trial$rt_col<1000 & fam_trial$rt_col>-1000), ] #only accept answers in range of -1000 < x < 1000

list_vsl_id <- unique(mean_table$id)

for(id in list_vsl_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  mean_table$rt_col_scale[mean_table$id==id]<-scale(mean_table$rt_col[mean_table$id==id])
  rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
  rt_slope_scale <-append(rt_slope_scale,round(summary(lm(mean_table$rt_col_scale[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
  hit_rate<-append(hit_rate,round(sum(!is.na(mean_table$rt_col[mean_table$id==id]))/total_vsl_trial,digits =2))
  miss_rate<-append(miss_rate,round(sum(fam_trial$rt_col[fam_trial$id==id]==-1)/total_vsl_trial,digits=2))
  correct_rejection <- append(correct_rejection, round(sum(fam_block$rt[fam_block$par_id==id]==-1 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/264,digits=3)) #264 is the total number of stimuli in the familiarization block
  false_alarm <- append(false_alarm, round(sum(fam_block$rt[fam_block$par_id==id]!=-1 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/264,digits=3))
}

subj_table <- data.frame(list_vsl_id,mean_rt, rt_slope,rt_slope_scale,hit_rate, miss_rate,correct_rejection,false_alarm)
dprime<-NULL
for (i in seq(from=1,to=length(subj_table$list_vsl_id),by=1)){dprime<-append(dprime,qnorm(subj_table[i,]$hit_rate-0.00000001)-qnorm(subj_table[i,]$false_alarm+0.000000001))} #minus 0.000000001 to avoid perfect hit rate
subj_table$dprime <- dprime

#colnames(subj_table) <- c("VSL_ID","mean_rt", "rt_slope","hit", "miss","corr_rejection","false_alarm","dprime")
#print(kable(subj_table,format = "pandoc"))

group <- NULL
for (i in seq(from=1,to=length(subj_table$list_vsl_id),by=1))
    {if (subj_table[i,]$list_vsl_id %in% TYP)
    {group[i]<-"TYP"}
    else if (subj_table[i,]$list_vsl_id %in% DD)
    {group[i] <- "DD"}}
subj_table$group <- group

return(subj_table)
}
```

* The DD group had a faster RT acceleration than the TYP group tested by linear regression model
```{r,echo=FALSE,warning=FALSE}
fam_trial_vsl <- compute_visual()
subj_table_vsl <- get_subj_visual()
model1 <- lm(rt_col~reindex*group_cond,data=fam_trial_vsl)
print(summary(model1))
fam_trial_vsl_scale <- compute_visual_scale()
model1_scale <- lm(rt_col~reindex*group_cond,data=fam_trial_vsl_scale)
print(summary(model1_scale))
```
* marginal results with the raw RT data and significant results (same as linear regression) with the scaled data tested by lmer.
```{r,echo=FALSE,warning=FALSE}
library(lmerTest)
model2 <- lmer(rt_col~group_cond*reindex + (1|id)+(0+reindex|id),data=fam_trial_vsl)
print(summary(model2))
model2_scale <- lmer(rt_col~group_cond*reindex + (1|id)+(0+reindex|id),data=fam_trial_vsl_scale)
print(summary(model2_scale))
```
##Plot of VSL RT
### RT as the function of Target repetition
```{r,echo=FALSE}
library(reshape)
library(reshape2)
group_rt_mean_vsl = cast(fam_trial_vsl,reindex+group_cond~.,value="rt_col",mean)
colnames(group_rt_mean_vsl)[3]="mean_RT"
group_rt_sd_vsl = cast(fam_trial_vsl,reindex+group_cond~.,value="rt_col",sd)
colnames(group_rt_sd_vsl)[3]="sd_RT"
group_rt_length_vsl = cast(fam_trial_vsl,reindex+group_cond~.,value="rt_col",length)
colnames(group_rt_length_vsl)[3]="length"
group_rt_vsl = merge(group_rt_mean_vsl,group_rt_sd_vsl)
group_rt_vsl = merge(group_rt_vsl,group_rt_length_vsl)
group_rt_vsl$se = group_rt_vsl$sd/sqrt(group_rt_vsl$length)
summary(group_rt_vsl)
pd <- position_dodge(0.2)
ggplot(group_rt_vsl,aes(x = reindex,y = mean_RT,colour = group_cond)) +
  theme_classic(base_size = 20.0) +
  xlab(label = 'Trial Index') +
  ylab(label = 'Response time during\n VSL Familiarization (ms)') +
  scale_x_continuous(breaks = pretty_breaks()) +
  scale_y_continuous(breaks = pretty_breaks(),limits=c(300,550)) +
  scale_colour_hue(name="Group",    # Legend label, use darker colors
                     breaks=c("DD", "TYP"),
                     labels=c("Dyslexia", "Typical"),
                     l=40) +
  #scale_colour_brewer(palette = 'Set1') +
  geom_point(position=pd,shape = 23, size = 3) +
  geom_errorbar(position=pd,aes(ymin = mean_RT-se, ymax = mean_RT+se),width=0.1)+
  geom_line(position=pd)+
  theme(legend.justification=c(1,0),legend.position=c(1,0))  
```
###Boxplot of the first half of the trials is significantly greater than the latter half of the trial
```{r,echo=FALSE}
par(mfrow=c(1,2))
boxplot(fam_trial_vsl_scale$rt_col[fam_trial_vsl_scale$reindex<total_vsl_trial/2], main="RT - first half of the trials",col="deepskyblue4",ylim=c(-4,4))
boxplot(fam_trial_vsl_scale$rt_col[fam_trial_vsl_scale$reindex>total_vsl_trial/2], main="RT - latter half of the trials",col="deepskyblue4",ylim=c(-4,4))
```
### plot mean RT slope across the two groups
* mean RT slope
```{r,echo=FALSE}
cbbPalette <- c("#000000","#000000")
ggplot() +
  geom_bar(aes(x = group,y = rt_slope,fill = group),data=subj_table_vsl,colour = '#000000',fun.data = mean_sdl,fun.args = list(mult = 1),stat = 'summary',position = position_dodge(width = 0.9)) +
  theme_classic(base_size = 18.0) +
  ylab(label = 'Response Time Slope (ms/Trial)') +
  xlab(label = 'Group') +
  #coord_cartesian(ylim = c(0.3,1)) +
  geom_errorbar(aes(y = rt_slope, x = group),data=subj_table_vsl,size = 0.3,width = 0.2,fun.y = function(x) mean(x),fun.ymin = function(x) mean(x) - sd(x)/sqrt(length(x)),fun.ymax = function(x) mean(x) + sd(x)/sqrt(length(x)) ,stat = 'summary')+
  geom_beeswarm(aes(x = group,y = rt_slope, colour = group),data=subj_table_vsl,dodge.width=0.9,cex=2.5) +
  scale_fill_brewer(palette = 'Set1') + 
  scale_color_manual(values=cbbPalette)
```
* mean RT slope scaled
```{r,echo=FALSE}
ggplot() +
  geom_bar(aes(x = group,y = rt_slope_scale,fill = group),data=subj_table_vsl,colour = '#000000',fun.data = mean_sdl,fun.args = list(mult = 1),stat = 'summary',position = position_dodge(width = 0.9)) +
  theme_classic(base_size = 18.0) +
  ylab(label = 'Scaled Response Time Slope\n(au/trial)') +
  xlab(label = 'Group') +
  #coord_cartesian(ylim = c(0.3,1)) +
  geom_errorbar(aes(y = rt_slope_scale, x = group),data=subj_table_vsl,size = 0.3,width = 0.2,fun.y = function(x) mean(x),fun.ymin = function(x) mean(x) - sd(x)/sqrt(length(x)),fun.ymax = function(x) mean(x) + sd(x)/sqrt(length(x)) ,stat = 'summary')+
  geom_beeswarm(aes(x = group,y = rt_slope_scale, colour = group),data=subj_table_vsl,dodge.width=0.9,cex=2.5) +
  scale_fill_brewer(palette = 'Set1') + 
  scale_color_manual(values=cbbPalette)
```

#Compute RT for TSL
* The two groups are not different in the target detection task
* Neither group showed a significant negative RT slope.
```{r,echo=FALSE}
compute_aud <- function(data)
{
rt_col <- NULL
id <- NULL
trial <- NULL
target <- NULL
group_cond <- NULL
row_number <- which(tsl$targ==tsl$stimulus)
for (i in row_number){
  #the audio plays 100ms after the trial begins, and the trial lasts 480ms, hence the number
        if (tsl[i,]$rt > 0){rt_col <- append(rt_col,tsl[i,][,"rt"]-100)} 
        if (tsl[i,]$rt < 0){rt_col <- append(rt_col,100-tsl[i,][,"rt"]-100)}
        trial <- append(trial,tsl[i,][,"trial_index"])
        id <- append(id,tsl[i,]$par_id)
         group_cond <- append(group_cond,tsl[i,]$group)
   if (tsl[i+1,][,"rt"]!=-1000 & tsl[i+1,][,"rt"]<0){
        rt_col[(match(i,row_number))] <- 380-tsl[i+1,][,"rt"]}
    
    if (tsl[i-1,][,"rt"]>0){
        rt_col[(match(i,row_number))] <- 480-tsl[i-1,][,"rt"]}
   if (tsl[i+1,][,"rt"]!=-1000 & tsl[i+1,][,"rt"]>0){
    rt_col[(match(i,row_number))] <- 580+tsl[i+1,][,"rt"]}
         
    }

 
rt_df1 <- data.frame(trial,rt_col,id,group_cond)
fam_block <- tsl[which(tsl$trial_index<603 & tsl$trial_index>26),] #fam block in tsl starts at index 27 and ends at index 602
fam_trial <- rt_df1[which(rt_df1$trial<603 & rt_df1$trial>26), ]

reindex <- rep(1:total_tsl_trial,total_participant)
fam_trial$reindex <- reindex
fam_trial <- fam_trial[which(!is.na(fam_trial$group_cond)),]

mean_table <- fam_trial[which(fam_trial$rt_col!=-1000),]
mean_table <- fam_trial[which(fam_trial$rt_col<960 & fam_trial$rt_col>-960), ] #only accepts answer in range of -380 < x < 580 (one stimulus before and one stimulus after the target)
hit_rate <- NULL
miss_rate <- NULL
correct_rejection <- NULL
false_alarm <- NULL
mean_rt <- NULL
rt_slope <- NULL
list_tsl_id <- unique(mean_table$id)

for(id in list_tsl_id){
  mean_rt<-append(mean_rt,round(mean(mean_table$rt_col[mean_table$id==id]),digits=3))
  rt_slope <-append(rt_slope,round(summary(lm(mean_table$rt_col[mean_table$id==id]~mean_table$reindex[mean_table$id==id]))$coefficient[2,1],digits=3))
  hit_rate<-append(hit_rate,round(sum(mean_table$rt_col[mean_table$id==id]!=-1000)/total_tsl_trial,digits =2))
  miss_rate<-append(miss_rate,round(sum(fam_trial$rt_col[fam_trial$id==id]==-1000 | fam_trial$rt_col[fam_trial$id==id]<=-480 | fam_trial$rt_col[fam_trial$id==id]>960)/total_tsl_trial,digits=2))
  correct_rejection <- append(correct_rejection, round(sum(fam_block$rt[fam_block$par_id==id]==-1000 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/528,digits=2)) #528 is the total number of stimuli in the fam block
  false_alarm <- append(false_alarm, round(sum(fam_block$rt[fam_block$par_id==id]!=-1000 & fam_block$targ[fam_block$par_id==id]!=fam_block$stimulus[fam_block$par_id==id])/528,digits=2))
}


subj_table <- data.frame(list_tsl_id,mean_rt, rt_slope,hit_rate, miss_rate,correct_rejection,false_alarm)
dprime<-NULL
for (i in seq(from=1,to=length(subj_table$list_tsl_id),by=1)){dprime<-append(dprime,qnorm(subj_table[i,]$hit_rate-0.00000001)-qnorm(subj_table[i,]$false_alarm))}
subj_table$dprime <- dprime

#colnames(subj_table) <- c("TSL_ID","mean_rt", "rt_slope","hit", "miss","corr_rejection","false_alarm","dprime")

#print(kable(subj_table))
group <- NULL
for (i in seq(from=1,to=length(subj_table$list_tsl_id),by=1))
    {if (subj_table[i,]$list_tsl_id %in% TYP)
    {group[i]<-"TYP"}
    else if (subj_table[i,]$list_tsl_id %in% DD)
    {group[i] <- "DD"}}
subj_table$group <- group
model3 <- wilcox.test(dprime~group,data=subj_table)
print(model3)
print(t.test(subj_table$rt_slope[subj_table$group=="DD"],mu=0,alternative="less"))
print(t.test(subj_table$rt_slope[subj_table$group=="TYP"],mu=0,alternative="less"))
return(mean_table)
}
```
* the two groups are not different in RT slope.
```{r,echo=FALSE,warning=FALSE}
fam_trial_tsl <- compute_aud()
model1 <- lm(rt_col~reindex*group_cond,data=fam_trial_tsl)
print(summary(model1))
model2 <- lmer(rt_col~reindex*group_cond+(1|id)+(0+reindex|id),data=fam_trial_tsl)
summary(model2)
```

##Plot of TSL RT
```{r,echo=FALSE}
ggplot() +
  theme_classic(base_size = 20.0) +
  xlab(label = 'Trial Index') +
  ylab(label = 'Response time (ms) during\n TSL Familiarization') +
  scale_x_continuous(breaks = pretty_breaks()) +
  scale_y_continuous(breaks = pretty_breaks()) +
  geom_point(aes(x = reindex,y = rt_col,colour = group_cond),data=fam_trial_tsl,shape = 23, size = 3) +
  geom_smooth(aes(x = reindex,y = rt_col,colour = group_cond),data=fam_trial_tsl,method = 'lm',formula = 'y ~ x',se = FALSE)
```

###Boxplot of the first half of the trials is significantly greater than the latter half of the trial
```{r,echo=FALSE}
par(mfrow=c(1,2))
boxplot(fam_trial_tsl$rt_col[fam_trial_tsl$reindex<total_tsl_trial/2], main="RT - first half of the trials",col="deepskyblue4")
boxplot(fam_trial_tsl$rt_col[fam_trial_tsl$reindex>total_tsl_trial/2], main="RT - latter half of the trials",col="deepskyblue4")
```

#Plot by group[consider normalizing RT within each participant and computer RT slope]
```{r,fig.width=10, fig.height=6, echo=FALSE}
DD_mean_vsl <- NULL
DD_mean_tsl <- NULL
DD_tsl_hit_rate <- NULL
DD_vsl_hit_rate <- NULL
TYP_mean_vsl <- NULL
TYP_mean_tsl <- NULL
TYP_tsl_hit_rate <- NULL
TYP_vsl_hit_rate <- NULL
number_DD <- NULL
number_TYP <- NULL

for(id in DD){
  DD_mean_vsl<- mean(append(DD_mean_vsl,round(mean(fam_trial_vsl$rt_col[fam_trial_vsl$id==id]))),na.rm=TRUE)
  DD_mean_tsl<- mean(append(DD_mean_tsl,round(mean(fam_trial_tsl$rt_col[fam_trial_tsl$id==id]))),na.rm=TRUE)
  DD_vsl_hit_rate<-round(mean(append(DD_vsl_hit_rate,round(sum(fam_trial_vsl$rt_col[fam_trial_vsl$id==id]!=-1)/total_vsl_trial,digits =2)),na.rm=TRUE),digits=2)
  DD_tsl_hit_rate<-round(mean(append(DD_tsl_hit_rate,round(sum(fam_trial_tsl$rt_col[fam_trial_tsl$id==id]!=-1000)/total_tsl_trial,digits =2)),na.rm=TRUE),digits=2) 
  number_DD <- length(intersect(list_vsl_id, DD))
}

for(id in TYP){
  TYP_mean_vsl<-mean(append(TYP_mean_vsl,round(mean(fam_trial_vsl$rt_col[fam_trial_vsl$id==id]))),na.rm=TRUE)
   TYP_mean_tsl<-mean(append(TYP_mean_tsl,round(mean(fam_trial_tsl$rt_col[fam_trial_tsl$id==id]))),na.rm=TRUE)
  TYP_vsl_hit_rate<-round(mean(append(TYP_vsl_hit_rate,round(sum(fam_trial_vsl$rt_col[fam_trial_vsl$id==id]!=-1)/total_vsl_trial,digits =2)),na.rm=TRUE),digits=2)
  TYP_tsl_hit_rate<-round(mean(append(TYP_tsl_hit_rate,round(sum(fam_trial_tsl$rt_col[fam_trial_tsl$id==id]!=-1000)/total_tsl_trial,digits =2)),na.rm=TRUE),digits=2)
  number_TYP <- length(intersect(list_vsl_id, TYP))
}

DD_col <- rbind(DD_mean_tsl,DD_mean_vsl,DD_tsl_hit_rate,DD_vsl_hit_rate,number_DD)
TYP_col <- rbind(TYP_mean_tsl,TYP_mean_vsl,TYP_tsl_hit_rate,TYP_vsl_hit_rate,number_TYP)
compare_table <- cbind(DD_col,TYP_col)
colnames(compare_table) <- c("Dylexia","Typical")
rownames(compare_table) <- c("RT_TSL","RT_VSL","Hit_rate_tsl","Hit_rate_vsl","Number of participants")
#print(kable(compare_table))
par(mfrow=c(1,2))

#Plot 
qplot(reindex,rt_col,data=fam_trial_vsl,facets=(. ~ fam_trial_vsl$group_cond),color= group_cond, main="VSL RT by group", ylab="Response time", xlab="Trial index") + geom_smooth(method='lm') + scale_color_discrete(name="Group",labels=c("Dylexia","Typical"))
qplot(reindex,rt_col,data=fam_trial_tsl,facets=(. ~ fam_trial_tsl$group_cond),color= group_cond,main="TSL RT by group",ylab="Response time", xlab="Trial index") + geom_smooth(method='lm') + scale_color_discrete(name="Group",labels=c("Dylexia","Typical"))

```

#Compute accuracy
```{r,echo=FALSE,warning=FALSE}
vsl_acc <- vsl[which(vsl$trial_index<614 & vsl$trial_index>309),] #the test block starts and ends with this index
tsl_acc <- tsl[which(tsl$trial_index<831 & tsl$trial_index>608),]
vsl_cond <- NULL
for (i in seq(from=1,to=length(vsl$cond),by=length_vsl)){vsl_cond<-append(vsl_cond,as.character(vsl[i,]$cond))}
tsl_cond <- NULL
for (i in seq(from=1,to=length(tsl$cond),by=length_tsl)){tsl_cond<-append(tsl_cond,as.character(tsl[i,]$cond))}

ans <- NULL
keyv <- NULL
subj <- NULL
cond<- NULL

#Extract the response for the 2AFC task
#vsl acc
  row_numberv <- which(vsl_acc$key_press != -1 & vsl_acc$stimulus=="")
  for (i in row_numberv){
    ans<-append(ans,vsl_acc[i,]$key_press)
    subj <- append(subj,vsl_acc[i,]$par_id)
    cond <- append(cond,vsl_acc[i,]$group)
  }
  
vsl_accuracy <- data.frame(ans,subj,cond)

#tsl acc
ans <- NULL
keyt <- NULL
subj <- NULL
cond<- NULL

row_numbert <- which(tsl_acc$key_press != -1 & (tsl_acc$trial_index-613)%%7==0) #since there is no stimuli recorded for the test block of tsl, we can only get the correct answer by counting the index. The test starts at 613 and the response begins every 7 index after that
  for (i in row_numbert){
    ans<-append(ans,tsl_acc[i,]$key_press)
    subj <- append(subj,tsl_acc[i,]$par_id)
   cond <- append(cond,vsl_acc[i,]$group)

  }
 
tsl_accuracy <- data.frame(ans,subj,cond)

#Match the language condition with the correct answer key
for(cond in vsl_cond){
    if (cond=="lang1"){keyv<-append(keyv,language_1)}
    else if (cond=="lang2"){keyv<-append(keyv,language_2)}}

for(cond in tsl_cond){
    if (cond=="lang1"){keyt<-append(keyt,language_1)}
    else if (cond=="lang2"){keyt<-append(keyt,language_2)}}



vsl_accuracy$key <- keyv
tsl_accuracy$key <- keyt

#Substitute the key press (49,50) with the answer (1,2)
vsl_accuracy$ans <- gsub(50,2,vsl_accuracy$ans)
vsl_accuracy$ans <- gsub(49,1,vsl_accuracy$ans)

tsl_accuracy$ans <- gsub(37,1,tsl_accuracy$ans)
tsl_accuracy$ans <- gsub(39,2,tsl_accuracy$ans)

corr <- NULL
corrt <- NULL

#Loop through and count the correct answer
for (i in seq(from=1,to=length(vsl_accuracy$ans),by=1)) {corr<-append(corr,as.numeric(vsl_accuracy[i,]$ans==vsl_accuracy[i,]$key))}
vsl_accuracy$corr <- corr
subj_corr <- NULL
for (id in list_vsl_id) {subj_corr <- append(subj_corr,round(sum(vsl_accuracy$corr[vsl_accuracy$subj==id])/total_test_trial,digits=3))}
vsl_acc_table <- data.frame(list_vsl_id,subj_corr,vsl_cond)

for (i in seq(from=1,to=length(tsl_accuracy$ans),by=1)) {corrt<-append(corrt,as.numeric(tsl_accuracy[i,]$ans==tsl_accuracy[i,]$key))}
tsl_accuracy$corr <- corrt
subj_corrt <- NULL
for (id in list_tsl_id) {subj_corrt <- append(subj_corrt,round(sum(tsl_accuracy$corr[tsl_accuracy$subj==id])/total_test_trial,digits=3))}
tsl_acc_table <- data.frame(list_tsl_id,subj_corrt,tsl_cond)

#Look into group performance between Dyl and Typ
DD_acc_vsl <- NULL
DD_acc_tsl <- NULL
TYP_acc_vsl <- NULL
TYP_acc_tsl <- NULL

for(id in DD){
  DD_acc_vsl<- append(DD_acc_vsl,vsl_acc_table$subj_corr[vsl_acc_table$list_vsl_id==id])
  DD_acc_tsl<- append(DD_acc_tsl,tsl_acc_table$subj_corr[tsl_acc_table$list_tsl_id==id])
}

for(id in TYP){
  TYP_acc_vsl<- append(TYP_acc_vsl,vsl_acc_table$subj_corr[vsl_acc_table$list_vsl_id==id])
  TYP_acc_tsl<- append(TYP_acc_tsl,tsl_acc_table$subj_corr[tsl_acc_table$list_tsl_id==id])
}
mean_DD_vsl <- mean(DD_acc_vsl,na.rm=TRUE)
mean_DD_tsl <- mean(DD_acc_tsl,na.rm=TRUE)
mean_TYP_vsl <- mean(TYP_acc_vsl,na.rm=TRUE)
mean_TYP_tsl <- mean(TYP_acc_tsl,na.rm=TRUE)
DD_acc_col <- rbind(mean_DD_tsl,mean_DD_vsl)
TYP_acc_col <- rbind(mean_TYP_tsl,mean_TYP_vsl)
compare_acc_table <- cbind(DD_acc_col,TYP_acc_col)
colnames(compare_acc_table) <- c("Dylexia", "Typical")
rownames(compare_acc_table) <- c("TSL accuracy","VSL accuracy")




#Simple t test

t.test(DD_acc_vsl,mu=0.5,alternative = "greater")
t.test(DD_acc_tsl,mu=0.5,alternative = "greater")

t.test(TYP_acc_vsl,mu=0.5,alternative = "greater")
t.test(TYP_acc_tsl,mu=0.5,alternative = "greater")

```


```{r,echo=FALSE}

##VSL Accuracy across subjects


#print(kable(vsl_acc_table))
```


```{r,echo=FALSE}
##TSL Accuracy across subjects

#print(kable(tsl_acc_table))
```

#A t-test to compare between Dylexia and Typical group
##In tsl
```{r,echo=FALSE}
t.test(DD_acc_tsl,TYP_acc_tsl)
```

##In vsl
```{r,echo=FALSE}
t.test(DD_acc_vsl,TYP_acc_vsl)
```

```{r,echo=FALSE}
# A line plot to compare mean accuracy of each group accross 32 trials

 index <- rep(1:total_test_trial,total_participant)
indx <- c(1:total_test_trial)
vsl_accuracy$index <- index
tsl_accuracy$index <- index
DD_vsl_point <- NULL
TYP_vsl_point <- NULL
DD_tsl_point <- NULL
TYP_tsl_point <- NULL
for (i in indx){DD_vsl_point <- append(DD_vsl_point,mean(vsl_accuracy$corr[vsl_accuracy$index==i & vsl_accuracy$cond=="DD"]))
DD_tsl_point <- append(DD_tsl_point,mean(tsl_accuracy$corr[tsl_accuracy$index==i & tsl_accuracy$cond=="DD"]))
TYP_tsl_point <- append(TYP_tsl_point,mean(tsl_accuracy$corr[tsl_accuracy$index==i & tsl_accuracy$cond=="TYP"]))
TYP_vsl_point <- append(TYP_vsl_point,mean(vsl_accuracy$corr[vsl_accuracy$index==i & vsl_accuracy$cond=="TYP"]))}
DDi <- rep("DD",total_test_trial)
Ti <- rep("TYP",total_test_trial)
dv <- cbind(DD_vsl_point,indx,DDi)
tv <- cbind(TYP_vsl_point,indx,Ti)
dt <- cbind(DD_tsl_point,indx,DDi)
tt <- cbind(TYP_tsl_point,indx,Ti)
vtable <- data.frame(rbind(dv,tv))
ttable <- data.frame(rbind(dt,tt))

#ggplot(data=vtable,aes(x=as.numeric(indx),y=as.numeric(paste(DD_vsl_point)), color=DDi,group=DDi),ylim=c(0,1)) + geom_point() + geom_line() + ggtitle("Accuracy accross trials in VSL") + xlab("Trial index")+ylab("Accuracy (%)") + scale_color_discrete(name="Group",labels=c("Dylexia","Typical"))
#ttable <- data.frame(rbind(dt,tt))
#ggplot(data=ttable,aes(x=as.numeric(indx),y=as.numeric(paste(DD_tsl_point)), color=DDi,group=DDi),ylim=c(0,1)) + geom_point() + geom_line() + ggtitle("Accuracy accross trials in TSL") + xlab("Trial index")+ylab("Accuracy (%)") + scale_color_discrete(name="Group",labels=c("Dylexia","Typical"))
```

#A box plot to compare the average accuracy between each group
```{r,fig.width=10, fig.height=10, echo=FALSE}
par(mfrow=c(2,2))
boxplot(DD_vsl_point, main="Dylexia-VSL",col="deepskyblue4", pars=list(ylim=c(0.2,1)))
boxplot(TYP_vsl_point, main="Typical-VSL",col="deepskyblue4", pars=list(ylim=c(0.2,1)))

boxplot(DD_tsl_point, main="Dylexia-TSL",col="deepskyblue4", pars=list(ylim=c(0.2,1)))

boxplot(TYP_vsl_point, main="Typical-TSL",col="deepskyblue4", pars=list(ylim=c(0.2,1)))

ggplot() +
	geom_bar(aes(x = Task,y = Accuracy,fill = Group),data=acc,colour = '#000000',fun.data = mean_sdl,fun.args = list(mult = 1),stat = 'summary',position = position_dodge(width = 0.9)) +
	ylab(label = 'Accuracy') +
	#coord_cartesian(ylim = c(0.3,1)) +
	geom_beeswarm(aes(x = factor(Task),y = Accuracy,colour = Group),data=acc,dodge.width=0.9,cex=2.5) +
	scale_colour_grey(guide = guide_legend(),start = 0.0,end = 0.0) +
scale_fill_manual(labels = c("Dylexia","Typical"),values = c("#b2182b", "#2166ac")) +	geom_hline(yintercept=0,linetype=2) +theme_classic(base_size = 20.0) + guides(color = FALSE) 

ggplot(acc1, aes(x=Task, y = Accuracy, fill=Group)) + geom_bar(stat = "identity",position=position_dodge()) + geom_errorbar(aes(ymin=Accuracy-se,ymax=Accuracy+se),width=.1,size=.8,position=position_dodge(.9)) + ggtitle("Accuracy plot") + scale_fill_grey(guide = guide_legend(),start = 0.4,end = 0.8) + geom_beeswarm(aes(x = factor(Task),y = Accuracy,colour = Group),data=acc,dodge.width=1,cex=2.5) + theme_classic(base_size = 20.0) + scale_colour_grey(guide = guide_legend(),start = 0.0,end = 0.0) 
# another way to plot
levels(acc$Task) = c("ASL","VSL")
acc$Task = factor(acc$Task,levels(acc$Task)[c(2,1)])
levels(acc$Group) = c("Dyslexia","Typical")
cbbPalette <- c("#000000","#000000")
ggplot() +
  geom_bar(aes(x = Task,y = Accuracy,fill = Group),data=acc,colour = '#000000',fun.data = mean_sdl,fun.args = list(mult = 1),stat = 'summary',position = position_dodge(width = 0.9)) +
  theme_classic(base_size = 20.0) +
  ylab(label = 'Test Accuracy') +
  coord_cartesian(ylim = c(0.3,1)) +
  geom_beeswarm(aes(x = Task,y = Accuracy, colour = Group),data=acc,dodge.width=0.9,cex=2.5) +
  scale_fill_brewer(palette = 'Set1') + 
  scale_color_manual(values=cbbPalette) +
  geom_hline(yintercept=0.5,linetype=2)

```
